\section{Candidate Preferences}
\subsection*{Preference 1 — Rajender Kumar Chaudhary}
\begin{tabularx}{\linewidth}{@{}lY lY@{}}
\textbf{Name} & Rajender Kumar Chaudhary & \textbf{Category/Caste} & OBC/Jat \\
\textbf{Age} & 54 & \textbf{Occupation} & Advocate & Farmer \\
\textbf{Education} & BA, LLB, LLM (Pursuing) & \textbf{Year Joined} & 1985 \\
\textbf{Phone} & ******9999 & \textbf{Record} &  \\
\end{tabularx}

\textbf{Rationale.} Belief in Congress ideology; long family history.

\textbf{Strengths.} College-days NSUI; administrative hold; strong proposer set.

\textbf{Weaknesses.} —

\textbf{Proposers.} Ram Singh (Ex HM, 5x MLA); Furkan Ahmed (MLA)

\textbf{Positions Held.} Ward President (2010–2015); DCC Member (2018–)

\textbf{Elections Contested.} Contested Nagar Palika 2019 (Won); Assembly 2022 (Runner-up)

\vspace{8pt}\hrule\vspace{10pt}

\subsection*{Preference 2 — Aasma Parveen}
\begin{tabularx}{\linewidth}{@{}lY lY@{}}
\textbf{Name} & Aasma Parveen & \textbf{Category/Caste} & General/Sheikh \\
\textbf{Age} & 42 & \textbf{Occupation} & School Teacher \\
\textbf{Education} & MA (Education) & \textbf{Year Joined} & 2007 \\
\textbf{Phone} & ******6789 & \textbf{Record} &  \\
\end{tabularx}

\textbf{Rationale.} Strong grassroots rapport in wards 4–7; education focus.

\textbf{Strengths.} Clean image; women’s SHG networks; good booth mobilization.

\textbf{Weaknesses.} Limited funding base.

\textbf{Proposers.} Pradeep Kumar (Councillor); Neelam Devi (ZP Member)

\textbf{Positions Held.} Ward Education Committee (2015–2019)

\textbf{Elections Contested.} Contested Ward 6 (Won 2019)

\vspace{8pt}\hrule\vspace{10pt}

\subsection*{Preference 3 — Vikram Singh}
\begin{tabularx}{\linewidth}{@{}lY lY@{}}
\textbf{Name} & Vikram Singh & \textbf{Category/Caste} & SC/Chamar \\
\textbf{Age} & 39 & \textbf{Occupation} & Small Business Owner \\
\textbf{Education} & B.Com & \textbf{Year Joined} & 2010 \\
\textbf{Phone} & ******2345 & \textbf{Record} &  \\
\end{tabularx}

\textbf{Rationale.} Entrepreneur; youth outreach; logistics support.

\textbf{Strengths.} Strong unions connect; event organization; transport assets.

\textbf{Weaknesses.} New to party committees.

\textbf{Proposers.} Mahesh Ram (Ex DCC Gen Secy); Poonam Bala (PCC Member)

\textbf{Positions Held.} Block Youth President (2021–)

\textbf{Elections Contested.} First-time contender

\vspace{8pt}\hrule\vspace{10pt}
